\chapter{Conclusion}\label{sec:thesis_conclusion}

This thesis began with the goal of improving the robustness of gait with
transfemoral prostheses so as to reduce amputees' risk of falling and increase
their quality of life. Towards this goal, we started by comparing a proposed
neuromuscular strategy for transfemoral prosthesis control to the established
impedance control strategy. We attempted to make this comparison as objective as
possible by building a robotic prosthesis capable of accurate torque control
(\cref{sec:pros_design}) and developing methods that employ the user's feedback
to select prosthesis control parameters (\cref{sec:preference_optimization}).
While the experiment comparing neuromuscular and impedance control did not
confirm our hypothesis that neuromuscular control would lead to a significant
reduction in falls (\cref{sec:nm_vs_imp}), it did clarify the importance of
state estimation in prosthesis control. This insight motivated the development
of swing and stance controllers with state estimation via an extended Kalman
filter (EKF) at the core of each
(\cref{sec:trip_avoidance,sec:phase_estimation}). The proposed swing controller
uses an EKF to estimate the position and orientation of the hip, which is then
used to plan knee and ankle swing trajectories that avoid trips. The proposed
stance controller uses an EKF to estimate the gait phase during stance. This
phase estimate made the gait robust to ground height disturbances and able to
adapt to both sudden and gradual changes in gait speed. 

In performing the work in this thesis, we have assembled a substantial amount of
practical knowledge and suggestions for future research in the field. First,
when it comes to prosthesis design, in hindsight, we likely put too much
emphasis on prosthesis performance and did not consider enough whether the user
would actually be able to make use of the performance. In our experiments,
able-bodied users wore the prosthesis through an L-shaped adapter
(\cref{fig:prosthesis_actual}) while amputees used their own socket
(\cref{fig:prosthesis_phase_exp}). Both of these interfaces are not very secure,
limiting the weight of the prosthesis and the dynamism of movements. Therefore,
while our prosthesis design, at \unit[6.8]{kg}, is of comparable mass to a
biological limb, it is too heavy to use comfortably for an extended period of
time. Future prosthesis designs should be mindful of the constraint the
interface places on useable torque and comfortable prosthesis mass. One solution
for a transfemoral prosthesis design for research purposes, which achieves high
performance and keeps weight to a minimum, is to create a knee-ankle prosthesis
emulator, similar to the ankle emulator created by
\citet{caputo2013experimental}.

A difficulty faced when conducting this research was the substantial time spent
implementing various controllers from the literature on our transfemoral
prosthesis prototype.  This challenge would be significantly reduced with
standardization of the interface between the low-level controls and the
mid-level behavior controls. Standardizing this interface would more easily
allow researchers to share code and try controllers on their own prostheses.
Standardizing the hardware design too would also help in this effort and
substantially decrease the time required to make progress in this field. The
recent development of open source knee and ankle prosthesis designs should help
significantly in this regard \citep{azocar2018design}.

Another development that would help decrease the time required to improve
prosthesis controls is better simulations of amputees and their interactions
with hardware. In \cref{sec:control_sim}, we presented results from one such
simulation that predicted more falls for impedance control than neuromuscular
control when walking on rough ground. Based on the experimental results on the
real prosthesis that we have gathered, it seems these simulations may have
overstated the potential improvement in gait robustness offered by neuromuscular
control. We may be able to improve these sorts of simulations to better predict
real-world results in two ways. First, through the course of conducting this
research, we have recorded large amounts of motion capture data of users walking
on the prosthesis. This data could be used to improve the neuromuscular model to
better capture actual subject responses to disturbances. Second, in
\cref{sec:control_sim}, we used the shooting method and a genetic algorithm
\citep{hansen2006cma} to optimize the control parameters of the prosthesis.
These optimizations often required days to converge on a solution. In future
work, more advanced simulation/trajectory optimization techniques should be
considered such as using symbolic differentiation to derive the change in the
control action with respect to parameters and using nonlinear programming and
collocation to directly solve the optimal control problem
\citep{hargraves1987direct}. 

A limitation of the studies we performed comparing the neuromuscular and
impedance controllers (\cref{sec:nm_vs_imp}) and comparing our proposed GP-EKF
control to the neuromuscular and impedance controllers
(\cref{sec:phase_estimation}) is that we only allowed participants to select
parameters for the different controllers from a discrete library of choices
generated by fitting controllers to set of able-bodied walking data. Using a
discrete set of parameters had the advantage of ensuring that the parameters
were sampled from the subspace that produces reasonable and safe walking gaits.
This is important on a prosthetic device especially, as a poor combination of
parameters can cause the prosthesis to behave erratically and fail to provide
support for the user. Moreover, it allowed us to circumvent performing
optimizations in the high dimensional space of controller parameters. However,
it is also possible that better parameters for each controller exist and that
they may have changed the outcomes of our comparisons had we used them. 

A potential solution for this limitation is to treat the able-bodied gait data
we use to generate parameters as a set of \emph{basis gaits}. We could then
perform continuous optimization of controller parameters in the gait space
spanned by this basis. For example, given $N$ basis gaits $\theta = [\theta_1,
\theta_2, \ldots, \theta_N]^T$, where each $\theta_n$ is a collection of gait
data for a specific subject, we could optimize over a vector of weights $w =
[w_1, w_2, \ldots, w_N]^T$. These weights would synthesize a new gait as
$\theta_\tn{new} = w^T \theta$ from which we could derive parameters using the
methods discussed in \cref{sec:param_gen_nm_imp,sec:ctrl_surfs}. These
parameters could be then be evaluated on the prosthesis. Performing the
optimization in this way could ensure that the optimization procedure selects
parameters from a safe subspace and would reduce the dimensionality of the
optimization to $N$, which could be selected to be feasible for the chosen
optimization algorithm. This proposed optimization approach would be feasible
for the impedance and GP-EKF controllers as we can generate parameters for these
two controllers from gait data in fractions of a second. However, it would not
be feasible with the neuromuscular controller as it can take many hours to find
neuromuscular parameters to match gait data.

Finally, an innovation provided by the planning-based swing control described in
\crefrange{sec:swing_control_planning_intro}{sec:swing_control_planning_discuss}
is that it considers environmental information in real-time within the mid-level
controller. The environmental information directly and precisely impacts the
trajectories that are generated during swing. In contrast, previous prosthesis
controllers that have considered environmental information have primarily only
done so at the high-level for gait mode recognition (see
\cref{sec:back_high_level_control}). These high-level strategies switch the
mid-level control parameters within a discrete set of options. Similarly, the
phase-based stance control described in
\crefrange{sec:swing_control_planning_intro}{sec:swing_control_planning_discuss}
can use information in real-time from multiple sensors on the prosthesis to
reason about the appropriate control action to take. These results motivate
further research into mid-level controllers that can directly act on more
sources of information. Doing so may allow prostheses to adapt more
appropriately to the user and environment and take a broader range of actions
that are better suited to the specific situation at hand. 

\section{Final Thoughts}

This dissertation moved the field forward by performing the first direct
comparison of prosthesis controllers on identical prosthesis hardware to explore
the pros and cons of different control methods. By performing this comparison,
we gained important insights that motivated further development of prosthesis
controllers that proactively avoid trips and can robustly estimate the gait
phase, thereby enabling rapid adaptation to changes in gait. Future researchers
should continue to attempt to compare prosthesis controllers directly, despite
the difficulties of implementing multiple prosthesis controllers and comparing
them objectively. Doing so will ensure that future control developments
continue to advance the state-of-the-art. 

In \cref{sec:intro_motivation} we detailed the difficulties faced by amputees
using passive prostheses including their high energy consumption
\citep{waters1976energy}, abnormal gait \citep{jaegers1995prosthetic}, and
increased rate of falls \citep{miller2001prevalence}. While the work presented
in this thesis has improved upon previously proposed powered prosthesis
controls, it remains unclear whether the proposed powered prosthesis controllers
can improve amputees' gait deficits compared to existing passive prostheses.
Therefore, future work should also try to compare powered prostheses to their
mechanically-passive counterparts. With such comparisons, we can begin to
evaluate whether powered prostheses are finally fulfilling their potential
ability to fully replace the lost biological limb.
